---
title: "Student Segmentation"
author: "Eli Nimy"
date: "2022-07-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




```{r}
# Open University Learning Analytics Dataset
library(oulad)

# Data Analyis and Visualisation
library(tidyverse)

# Statistical Summary
library(tigerstats)

# Gaussian mixture model (GMM)
library(mclust)

# Interactive ggplots
library(plotly)
```


## Student Virtual Learning Environment: Sum Clicks Analysis
- *code_module* – an identification code for a module.
- *code_presentation* - the identification code of the module presentation.
- *id_student* – a unique identification number for the student.
- *id_site* - an identification number for the VLE material.
- *date* – the date of student’s interaction with the material measured as the number of days since the start of the - module-presentation.
- *sum_click* – the number of times a student interacts with the material in that day.
```{r}
# Load student VLE data 
svle_df <- student_vle
svle_df %>% head()
```



```{r}
# Percentage of missing values
sum(is.na(svle_df$sum_click))/length(svle_df$sum_click) * 100
```




```{r}
favstats(svle_df$date)
```



```{r}
favstats(svle_df$sum_click)
```



#### Clicks Data
- The number of times a unique student interacted with material(s) throughout the day / week / month / term / semester/ year will be summed
- Since engagement behavior can change, the number of interaction will vary with different days / weeks or etc. As a student may have a 100 clicks in one week and 200 the next (showing higher/lower engagement) so clustering can be performed for different weeks
```{r}
clicks_df <- svle_df %>% 
  # filter(date >=-25 & date <= 269 & 
  # code_presentation %in% 2013J) %>%  Filter for the dashboard (days) and semester
  group_by(id_student) %>% 
  summarise(sum_click = sum(sum_click))
clicks_df %>% head()
```



```{r}
favstats(clicks_df$sum_click)
```


## GMM Model
```{r}
# Selecting clicks for modelling
gmm_df <- select(clicks_df, sum_click)
gmm_df %>% head()
```


- Optimal Number of Components: 7 and 25
```{r}
# Fit a GMM model
set.seed(1837)
start_time <- Sys.time()
gmm_model <- Mclust(gmm_df, G=6)
end_time <- Sys.time()
```



```{r}
# Execution Time
end_time - start_time
```



```{r}
print(gmm_model)
```



```{r}
# Summary table 
summary(gmm_model)
```



```{r}
# Cluster Means
gmm_model$parameters$mean
```


- Unceratinty: A probability expressing the degree of uncertainty in a student belonging to a group
```{r}
# Add clusters and uncertainty values to original dataset
clicks_df$cluster <- gmm_model$classification
clicks_df$uncertainty <- gmm_model$uncertainty
clicks_df %>% head()
```



```{r}
# Exclude scientific outputs
options(scipen=999)
# View data set
# View(clicks_df) 
```


# Probability of Student belonging to each cluster
```{r}
# Probability of a student belonging to a cluster
cluster_probabilitics <- gmm_model$z
colnames(cluster_probabilitics) <- paste0('cluster', 1:gmm_model$G)
options(scipen=999)
# Create probabilities data frame
cluster_probabilitics <- cluster_probabilitics %>%
  round(2) %>% 
  as.data.frame()
cluster_probabilitics %>% head()
```



- A table with the probability of a student belonging to each cluster, the cluster a student belongs to and the uncertainty with a student belonging to the particular cluster
```{r}
# Add cluster belonging of student
cluster_probabilitics$cluster <- clicks_df$cluster
cluster_probabilitics$uncertainty <- gmm_model$uncertainty
cluster_probabilitics$id_student <- clicks_df$id_student
cluster_probabilitics %>% head()
```


#### Cluster Mean Table
```{r}
cluster_mean_df <- as.data.frame(round(gmm_model$parameters$mean))
colnames(cluster_mean_df) <- "cluster_mean"
cluster_mean_df
# Rename rownames to cluster 
cluster_mean_df <- cbind(cluster = rownames(cluster_mean_df), cluster_mean_df)
# Remove rownames 
rownames(cluster_mean_df) <- NULL
cluster_mean_df 
```


#### Cluster Count Table
```{r}
# Obtain number of observations in each cluster. 
cluster_count_df <- clicks_df %>%
  group_by(cluster) %>%
  summarise(Number_of_students = n()) #%>% 
  # arrange(Number_of_students)
cluster_count_df
```


#### Cluster Statistics Table
```{r}
cluster_stats <- merge(cluster_mean_df, cluster_count_df) %>% arrange(cluster_mean)
cluster_stats 
```



#### Distribution of Probabilities in each cluster
```{r}
# probabilities <- select(cluster_probabilitics, -cluster, -uncertainty, -id_student) %>%
#   as.data.frame() %>%
#   mutate(id = row_number()) %>%
#   tidyr::gather(cluster, probability, -id)
# 
# ggplot(probabilities, aes(probability)) +
#   geom_histogram() +
#   facet_wrap(~ cluster, nrow = 6) 
```


## Cluster Analysis Tab
```{r}
library(apexcharter)
library(highcharter)
```



```{r}
hchart(cluster_stats, "column", hcaes(x = cluster, y = cluster_mean), dataLabels = list(enabled = TRUE),
       name = "Average No. of Clicks") %>% 
  hc_title(
    text = paste0("Average Number of Clicks for Each Engagement Level")
  ) %>% 
  hc_xAxis(title = list(text = "Engagement Level")) %>% 
  hc_yAxis(title = list(text = "Average Number of Clicks"))
```


```{r}
hchart(cluster_stats, "column", hcaes(x = cluster, y = Number_of_students), dataLabels = list(enabled = TRUE),
       name = "No of Students") %>% 
  hc_title(
    text = paste0("Number of Students in Each Engagement Level")
  ) %>% 
  hc_xAxis(title = list(text = "Engagement Level")) %>% 
  hc_yAxis(title = list(text = "Number of Students")) %>% 
  hc_exporting(
    enabled = TRUE)
```


```{r}
hchart(clicks_df$sum_click, color = "#B71C1C", name = "Clicks") %>% 
  hc_title(
    text = paste0("Distribution of Clicks")
  ) %>% 
  hc_xAxis(title = list(text = "Number of Students")) %>% 
  hc_yAxis(title = list(text = "Number of Clicks"))
```


- Add min, max, average statistical summary of uncertainty
```{r}
hchart(clicks_df$uncertainty, color = "#B71C1C", name = "Uncertainty") %>% 
  hc_title(
    text = paste0("Distribution of Engagement Level Assignment Uncertainty")
  ) %>% 
  hc_xAxis(title = list(text = "Uncertainty")) %>% 
  hc_yAxis(title = list(text = "Number of Students"))
```


```{r}
fig <- clicks_df %>%
  plot_ly(
    y = ~sum_click,
    type = 'violin',
    box = list(visible = T),meanline = list(visible = T), x0 = 'Clicks') 
fig <- fig %>%
  layout(
    title = "Distribution of Clicks",
    yaxis = list(title = "Number of Clicks", zeroline = F))
fig
```


## Instructional Methods Tab
```{r}
vle_df <- vle
vle_df
```



```{r}
# For fast data operations
library(data.table)
```



```{r}
# Merging the dataframes to link students with activities
svle_vle_df <- data.table::merge.data.table(student_vle, vle, by = "id_site")
svle_vle_df
```



```{r}
# Number of Times student accessed an activity 
activity_df <- svle_vle_df %>% 
  group_by(id_student,activity_type) %>% 
  summarise(activity_access_count = n()) %>% 
  as.data.frame()
activity_df
```



```{r}
clicks_activity_df <- merge.data.table(activity_df, clicks_df, by = "id_student")
clicks_activity_df
```


Activity Categories 
- Resources - resource, oucontent, folder, ouwiki, glossary, url
- Assessment - quiz, questionnaire, external quiz
- VLE Site/App - dualpane, repeatactivity, htmlactivity, sharedsubpage, ouelluminate, dataplus, page, homepage, forumng, subpage, oucollaborate 
```{r}
clicks_activity_df <- clicks_activity_df %>%
  mutate(vle_activity = case_when(grepl("resource", activity_type) ~ "Resource",
                       grepl("oucontent", activity_type) ~ "Resource",
                       grepl("url", activity_type) ~ "Resource",
                       grepl("ouwiki", activity_type) ~ "Resource",
                       grepl("glossary", activity_type) ~ "Resource",
                       grepl("folder", activity_type) ~ "Resource",
                       grepl("quiz", activity_type) ~ "Assessment",
                       grepl("questionnaire", activity_type) ~ "Assessment",
                       grepl("externalquiz", activity_type) ~ "Assessment",
                       grepl("subpage", activity_type) ~ "VLE Site/App",
                       grepl("forumng", activity_type) ~ "VLE Site/App",
                       grepl("page", activity_type) ~ "VLE Site/App",
                       grepl("oucollaborate", activity_type) ~ "VLE Site/App",
                       grepl("dataplus", activity_type) ~ "VLE Site/App",
                       grepl("homepage", activity_type) ~ "VLE Site/App",
                       grepl("ouelluminate", activity_type) ~ "VLE Site/App",
                       grepl("dualpane", activity_type) ~ "VLE Site/App",
                       grepl("repeatactivity", activity_type) ~ "VLE Site/App",
                       grepl("htmlactivity", activity_type) ~ "VLE Site/App",
                       grepl("sharedsubpage", activity_type) ~ "VLE Site/App")) 
clicks_activity_df
```



```{r}
# Number of occurrences for each activity 
table(clicks_activity_df$vle_activity)
```



```{r}
# Occurrences of activity types per cluster
clicks_activity_df %>% 
  group_by(cluster, vle_activity) %>%
  summarise(activity_access_count = n())
```



```{r}
activity_stats <- clicks_activity_df %>% 
  filter(cluster %in% 1) %>%
  group_by(cluster, activity_type) %>%
  summarise(activity_access_count = n()) %>% 
  mutate(activity_access_percent = round(activity_access_count / sum(activity_access_count) * 100, 2)) %>% 
  arrange(desc(activity_access_percent))
activity_stats
```



```{r}
hchart(activity_stats, "column", hcaes(x = activity_type, y = activity_access_percent), 
       dataLabels = list(enabled = TRUE, format = "{y}%"),
       name = "% of Students") %>% 
  hc_title(
    text = paste0("Percentage of Students that Access each VLE Activity in Engagement Level ", 1)
  ) %>% 
  hc_xAxis(title = list(text = "VLE Activity")) %>% 
  hc_yAxis(title = list(text = "Percentage (%) of Students")) %>% 
  hc_exporting(
    enabled = TRUE)
```


- source: https://www.datanovia.com/en/lessons/highchart-interactive-bar-plot-in-r/
- Color options are included
```{r}
# Comparison between engagement levels 
# Maximum number of comparison should be limited to 3 in dashboard
activity_stats <- clicks_activity_df %>% 
  filter(cluster %in% c(1,2, 3)) %>%
  group_by(cluster, activity_type) %>%
  summarise(activity_access_count = n()) %>% 
  mutate(activity_access_percent = round(activity_access_count / sum(activity_access_count) * 100, 1)) %>% 
  arrange(desc(activity_access_percent))

hchart(activity_stats, "column", hcaes(x = activity_type, y = activity_access_percent, group = cluster), 
       dataLabels = list(enabled = TRUE, format = "{y}"),
       stacking = "normal") %>% 
  hc_title(
    text = paste0("Percentage of Students that Access each VLE Activity in Engagement Level")
  ) %>% 
  hc_xAxis(title = list(text = "VLE Activity")) %>% 
  hc_yAxis(title = list(text = "Percentage (%) of Students")) %>% 
  hc_exporting(
    enabled = TRUE)
```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```





```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```





```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```





```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```





```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```





```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



